No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-17 main/LICS.tex
started prose for Section 5

	\item
The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
%
Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
%
Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
%
This is illustrated below.
\end{enumerate}
%
\[
	\kern-1pt \netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw \kern-1pt 
\]
%
\end{IEEEproof}

@@

\section{Proof nets and constraint graphs}

[[ NOTE: we should decide on notation for steps versus paths in permutation relations ]]

>>>>

	\item
The path starts with a jump $\edge bx$ from a $\named b\bot$ in $A$ (and $b\neq a$, $x\neq z$).
%
Let the path end with the jumps $\edge wc$ and $\edge dz$, and let $\links(a)=y$.
%
Then $\links'$ is obtained from $\links$ by changing: $\links'(c)=y$, $\links'(a)=z$, and $\links'(e)=w$ for every $\named e\bot$ such that $e\neq a$ and $\links(e)=z$, including $d$.
%
This is illustrated below.
\end{enumerate}
%
\[
	\netB yxwz \perm \netB yxyz \perm \netB zxyz \perm \netB zxyw
\]
%
\end{IEEEproof}

@@

\section{Encoding constraint graphs}

\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Hearn-Demaine-2008} is a simple graph-rewriting formalism, introduced as a convenient tool for \textsc{PSPACE}-hardness reductions.
%
A rewriting step is the reversal of a single edge in a \emph{constraint graph}, a graph with weighted, directed edges and an \emph{inflow constraint} on each vertex, preserving the condition that the total weight of the incoming edges of each vertex is at least its inflow constraint.
%
The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.

We will introduce minor adaptations to this formalism to suit our reduction to MLL proof equivalence.
%
Mainly, a constraint graph here will have \emph{undirected} edges, and a separate notion of \emph{configuration} imposes a direction on edges.
%
A constraint graph will then be encoded as a sequent, while a configuration corresponds to a linking.
%
In addition, a configuration will be allowed to be \emph{partial}, leaving some edges undirected, as long as the directed edges suffice to satisfy the inflow constraints.
